Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-05 manuscript.Rmd
march variable

---
title: "Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?"
output:
  html_document:
    df_print: paged
    theme: cerulean
---

@@

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE))
```

@@

>>>>

---
title: "Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?"
output:
  html_document:
    df_print: paged
---

@@

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE)) %>% 
  mutate(march_inaug = 0)

travel_time_sf[11122:11676, "march_inaug"] = 1
#entries 11122 to 11676
```

@@

```{r}
st_queen <- function(a, b = a) st_relate(a, b, pattern = "F***T****")

as.nb.sgbp <- function(x, ...) {
  attrs <- attributes(x)
  x <- lapply(x, function(i) { if(length(i) == 0L) 0L else i } )
  attributes(x) <- attrs
  class(x) <- "nb"
  x
}

Queen <- as.nb.sgbp(st_queen(travel_time_sf %>% filter(year == 2017, month==1, week==3)))
```

```{r warning=FALSE}
listW = nb2listw(Queen)
dc_sar = spautolm(formula = mean_travel_time ~ as.numeric(distance), data = travel_time_sf %>% filter(year == 2017, month==1, week==3), listw = listW, family = "SAR")

summary(nc_sar)
```

```{r}
# dc$sar_resid <- resid(dc_sar)
# 
# travel_time_sf %>%
#   ggplot()+
#   geom_sf(aes(fill = sar_resid))
```
